\documentclass[a4paper]{article}
\usepackage{wp-settings}

\begin{document}

\pagecolor{oldlace}

\title{Picolo: Fast, Fully decentralized, Globally distributed Open Database Network}
\author{Adi Kancherla \and Arunesh Mishra}
\date{May 6, 2018 \\\hfill \\version 1 (private release, work-in-progress)}
\maketitle
\begin{abstract}

Picolo is a fast, scalable, verifiable, fully-decentralized, globally distributed transaction oriented database for
Blockchain-based Applications. Picolo uses a probabilistic replication framework on top of DHTs to achieve a O(1)
lookup latency for most queries. Its the first and so-far only system of its kind to distribute data at a global
scale will full-decentralization and externally-consistent distributed transactions. Its design is tailored to
support Blockchain-based applications.

\begin{itemize}
    \item Allows for verifiable transaction logs.
    \item Token economics that gamify honest participation from nodes over malicious intent.
\end{itemize}

\end{abstract}


%-----------------------------------------------------------------------------
%  INTRODUCTION
%-----------------------------------------------------------------------------
\section{Introduction}\label{Sect:Introduction}


    \begin{itemize}
        \item What are Dapps. Dapps will grow, but need to store data.
        \item Solutions today provide file storage semantics which might not work for all application types.
        \item Introduce the database problem on the blockchain. What are the requirements for a decentralized database.
        \item Overview of current approaches and limitations (details in the Background and Related work section).
    \end{itemize}


\subsection{Picolo's Features}
\begin{itemize}
    \item Network layer Scales with O(log N) overhead for N nodes.
    \item Network lookup using O(1) amortized lookup cost for DHT.
    \item Horizontally scalable 
    \item Automated data sharding
    \item Transactions can be applied across rows, columns and tables across machines
    \item Client controlled replication and data placement
    \item Synchronous replication and external consistency, the strongest form of consistency any database can support
    \item SQL like interface
    \item Supports storage of typed data
    \item Supports semi-relational structure for tables
    \item Configurable backups and restore mechanisms
    \item Verifiable legder for transactions.
\end{itemize}

%-----------------------------------------------------------------------------
%  BACKGROUND SECTION
%-----------------------------------------------------------------------------
\section{Background}
    \begin{itemize}
    \end{itemize}

%-----------------------------------------------------------------------------
%  RELATED WORK SECTION
%-----------------------------------------------------------------------------
\section{Related Work}
\section{Overall Design}

    \begin{itemize}
        \item Overall Picolo architecture.
        \item Token economics.
    \end{itemize}
\section{Network Subsystem}

    \begin{itemize}
        \item DHT layer for lookup. Replication and caching for O(1) lookups for popular items.
        \item Token economics for incentivized participation.
        \item Building with BFT.
    \end{itemize}
\section{Database Subsystem}

\subsection{Cluster}
\subsection{Versioning}
\subsection{Replication and Token economics}
\subsection{Handling Failures}

Some factors that affect prices of cryptos are listed below. These factors are by no means exhaustive but provide a framework within which mechanisms to analyze them can be discussed. See the sub sections where some techniques are presented.
Factors affecting the prices of crypto assets:

%-----------------------------------------------------------------------------
%  CONCLUSIONS
%-----------------------------------------------------------------------------
\section{Conclusion}
Initial implementations of AI algorithms that analyze structured and unstructured data are discussed. Unstructured data is analyzed in two steps: first, at a unit level and second as a sequence by feeding it to an LSTM. Structured data consisting of live feed from exchanges, current and past bets on the platform amongst others is represented as a game state where an independent decision making agent learns to take actions that maximize its game score. A method of determining payouts to platform users is discussed where they are determined by the magnitude as well as the category of contribution.


%-----------------------------------------------------------------------------
%  BIBLIOGRAPHY
%-----------------------------------------------------------------------------
\bibliographystyle{unsrt}
\bibliography{./bib/picolo.bib}
\end{document}
